Fit models and plots

### 2023-02-09 Code/13_Check_Pooled_Data.Rmd
Pooled data analysis

@@

# set datadist
dd.pooled<-rms::datadist(cbind(pooled.data.to.be.imputed, continent.df))
options(datadist="dd.pooled")

@@

# fit model
f.mi.full.pooled <- Hmisc::fit.mult.impute(form.BS.Rec.5.pooled, cph, xtrans=imputed.pooled.data,
                                 data=pooled.data.to.be.imputed, n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
summary(f.mi.full.pooled)
anova(f.mi.full.pooled)
```

>>>>

# set datadist
options(datadist="dd.training")

@@

@@

# fit model
f.mi.full.pooled <- Hmisc::fit.mult.impute(form.BS.Rec.5.pooled, cph, xtrans=imputed.pooled.data,
                                 data=pooled.data.to.be.imputed, n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
summary(f.mi.full.pooled, Continent="Europe")
anova(f.mi.full.pooled)
```
